Landscape heterogeneity simulation figures

### 2018-05-22 Manuscript_figures_2017_12_12.Rmd
Remove directory specific references

#Set working directory of where to produce Figures
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures April 2018")
```

@@

## Figure S1
Random forest variable importance results from `party` package using cforest function
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Party Package May 2018")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures May 2018")
tiff("FigureS1_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()

>>>>

#Set working directory of where to produce Figures
setwd()
```

@@

## Figure S1
Random forest variable importance results from `party` package using cforest function
```{r}
#setwd()

@@

#setwd()
tiff("FigureS1_party.tiff", height =4.5, width =8.7, units = "cm", compression = "lzw", res = 1200)
#multiplot(A, B, C, cols=3)
prow
dev.off()
